---
title: "Penguin data visualisation"
author: "Ben Cresswell"
date: today
format: html
editor: visual
execute:
  echo: false
  warning: true
  message: true
---

# Load packages
```{r}
## install.packages("tidyverse") # Never hard code this in your scripts, only run once to install
library(tidyverse)
```


# Load data
Will use a source file to do this (show file briefly)

## Need to use correct file name/path
```{r}
# Incorrect
source("demo.R")
```

## Can use full path to file (if you want but bad practice!!!)
```{r}
source("/Users/jc504838/Science/Data & analysis/Teaching/MB5370 Techniques 1/ClassRepos/TIMS1_Demo1/code/demo1.R")
```

## Could set wd but also bad practice!!

WHY??
```{r}
setwd("/Users/jc504838/Science/Data & analysis/Teaching/MB5370 Techniques 1/ClassRepos/TIMS1_Demo1")
getwd()
```

## Best is to work in R projects and use relative file paths
```{r}
source("demo1.r")
```


# Prove we have a working dataset loaded by plotting!
```{r}
penguins |> 
  ggplot(aes(x = bill_length_mm, y = bill_depth_mm, colour = species)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal()
```



# Let's close this project and re-open the Qmd - what will happen?!?


